---
title: "Homework-26"
author: "HarrySecor"
date: "11/2/2022"
output: html_document
---

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(ggfortify)
```



```{r}
soil <- read.csv(here("Data", "soil_reduced-1.csv"), stringsAsFactors = T)
```

A. before we begin any analysis, we need to check out data for possible errors/outliers. let's begin with that.

```{r}
levels(soil$Forest)
```

B. let's check soil organic matter and soil calcium
Start with a histogram

```{r}
ggplot(soil, aes(x = SOM_percent)) + geom_histogram()
```

calcium ppm histogram

```{r}
ggplot(soil, aes(x = Ca_ppm)) + geom_histogram()
```

look at the data set through glimps and summary to see if there's andything off

```{r}
glimpse(soil)
summary(soil)
```


## 1. Is there a relationship between Soil organic matter (SOM, %) and soil calcium (Ca_ppm)?

both variables are continuous

```{r}
ggplot(soil, aes(x = SOM_percent, y = Ca_ppm, color = Forest)) + geom_point() + ylab("Ca ppm") + xlab("SOM %") + theme_bw()
```
From looking at the data, it appears there may be a weak positive relationship between SOM percent and calcium ppm

can I guess the slope or y-intercept?
slope c. 1000/53 = 18ish, y int c. -5? 0? right around there 

what statistical model fits these data?
Both response and predictor are continuous so linear regression seems appropriate

so, let's construct the model
```{r}
SOM_CA_mod <- lm(Ca_ppm ~ SOM_percent, data = soil)
```

now I need to check model assumptions before interpreting

```{r}
autoplot(SOM_CA_mod)
```

based on my observations of the autoplot results, I'm modestly comfortable that my data meet the lm() assumptions.

now look at model outcome
```{r}
anova(SOM_CA_mod)
summary(SOM_CA_mod)
```

we accept the null hypothesis


##2. Does the abundance of worms differ between Donnerville and the Kip Tract?

separate out Donnerville and Kip Tract 

```{r}
Q2 <- filter(soil, Forest == "DONNERVILLE" | Forest == "KIP TRACT")
```

check for possible outliers

```{r}
summary(Q2$Worms)
```

does not seem to be any outlires for Worms

```{r}
ggplot(Q2, aes(x = Worms)) + geom_histogram() + facet_wrap(~Forest)
```

from the histogram there does look to be some differences

the best plot to show worms is a box and whisker plot

```{r}
ggplot(Q2, aes(x = Forest, y = Worms)) + geom_boxplot() + geom_point(size = 4, color = 'lightgrey', alpha = 0.5)
```

for Donnerville the range is 1-3 with the mean of 2 and an IQR of 1-2
For the Kip track the range is 2-5 with the mean of 4 and an IQR of 2-5

```{r}
Q2lm <- lm(Worms ~ Forest, data = Q2)
autoplot(Q2lm)
```

WHY DID YOU RUN THIS AS A LINEAR MODEL? YOU HAVE COUNT DATA (NUMBER OF WORMS) SO THIS SHOULD BE A CHI-SQUARE TEST.

Normal Q-Q looks pretty good not too far off of the line
residual  vs fitted is almost identical to the line

chi2 test is the best for categorical and discrete

```{r}
chiWorm <- xtabs(Worms ~ Forest, data = Q2)

chisq.test(chiWorm)
summary(chiWorm)
```


with P-value < 0.05 we fail to reject the hypothesis


## 3. Does the abundance of soil Magnesium (Mg_ppm) differ between Peavine and South Hammond?

filter out the two forests in question

```{r}
Q3 <- filter(soil, Forest == "PEAVINE" | Forest == "SOUTH HAMMOND")
```

check for outliers in magesium

```{r}
summary(Q3$Mg_ppm)
```
there may be a possible outlier at the to of the range check with histogram

```{r}
ggplot(Q3, aes(x = Mg_ppm)) + geom_histogram() + facet_wrap(~Forest)
```

the outlier may be a little high but I think that its not worth taking out unless it is greatly affecting the data

next check a box and whisker plot

```{r}
ggplot(Q3, aes(x = Forest, y = Mg_ppm)) + geom_boxplot() + geom_point(size = 4, color = 'lightgrey', alpha = 0.5)
```

YOU DIDN'T SAY WHY YOU ARE RUNNING A LINEAR MODEL HERE. WHAT IS THE STRUCTURE OF THE DATA THAT MAKES THIS THE APPROPRIATE TEST?

```{r}
Q3lm <- lm(Mg_ppm ~ Forest, data = Q3)
autoplot(Q3lm)
```

the graphs of the data look good other than one or two outliers


a 2 sample t test is best again because its 2 categorical and ratio data

```{r}
t.test(Mg_ppm ~ Forest, data = Q3)
```

with a P-value > 0.05 we accept the null hypothesis


## 4. Does the abundance of zinc (Zn_ppm) differ among forests?

looking at all forests so just look at a summary of zink

```{r}
summary(soil$Zn_ppm)
```
there is a large difference between Q3 and max so there may be an outlier 

time for a histogram

```{r}
ggplot(soil, aes(x = Zn_ppm)) + geom_histogram()
```
there is an outlier at the top of the data spectrum but it is close enough to be a legitimate data point

Forests are Categorical and Zink is ratio

make a box plot with an understandable message

```{r}
ggplot(soil, aes(x = Zn_ppm, y = Forest)) + geom_boxplot() + geom_point(size = 4, color = 'lightgrey', alpha = 0.5)
```
now the highest measurement looks too much like an outlier as its in the location with the least Zn_ppm

```{r}
Q4lm <- lm(Zn_ppm ~ Forest, data = soil)
autoplot(Q4lm)
```

the graphs from autoplot look good with the exception of several outliers

the next test should be an ANOVA test as Forest has 9 categories and Zn_ppm is ratio data

GOOD

```{r}
anova(Q4lm)
summary(Q4lm) # starts at Call:
```

with a P-Value > 0.05 we accept the null hypothesis.
