---
title: "Problem-Set-2"
author: "HarrySecor"
date: "10/30/2022"
output: html_document
---

regular set up

```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

read the Halloween data

```{r}
halloween <- read.csv(here("Data", "Halloween_data_PS2.csv"))
```

clean up the data set by making sure all the names are the same so they read as one factor

```{r}
halloween$Costume[1:8] <- "Wonder woman" 

fixClown <- which(halloween$Costume == "clown"| halloween$Costume == "creepy clown") 
halloween$Costume[fixClown]<- "Creepy clown"

halloween$Costume[25:27] <- "Witch"
halloween$Costume[28:30] <- "Pirate" # didn't need to change this one  but thought it would look better

fixType <- which(halloween$Type == "scary")
halloween$Type[fixType] <- "Scary" 
halloween$Type[26] <- "Scary" # for some reason the other way didnt work for this one so I had to fix it like this

unique(halloween$Costume)

```

The reason "scary" did't work is there was one with a space after the word e.g. "scary " and your search didn't find it. Adjusting the `which()` would be a better fix than manual indexing.



make costume and type into factors

```{r}
halloween$Costume <- as.factor(halloween$Costume)
halloween$Type <- as.factor(halloween$Type)
```

look at some info about the data for fun

```{r}
summary(halloween)
dim(halloween)
names(halloween)
```

do not need next code fragment
was thingking that I could use these but then I relized I just over complicated the next step and really didn't need them

```{r}
#scary <- filter(halloween, Type == "Scary")
#notScary <- filter(halloween, Type == "Not scary")
WonderWoman <- filter(halloween, Costume == "Wonder Woman")
CreepyClown <- filter(halloween, Costume == "Creepy clown")
Unicorn <- filter(halloween, Costume == "Unicorn")
Rabbit <- filter(halloween, Costume == "Rabbit")
Witch <- filter(halloween, Costume == "Witch")
Pirate <- filter(halloween, Costume == "Pirate")
Mouse <- filter(halloween, Costume == "Mouse")
Zombie <- filter(halloween, Costume == "Zombie")
Mermaid <- filter(halloween, Costume == "Mermaid")
```

I tried to keep more of the data but that wasn't working when it came time to make the graph
tried to keep the two extra lines I removed due to the NA's but it caused errors to occur so gave up

```{r}
hw <- halloween[-c(4, 12, 29, 30),]
#hw <- halloween[-c(12, 30),]
#hw2 <- halloween[-c(4, 29),]
meanCostume <- summarise(group_by(hw, Costume), meanCandies = mean(candy_pieces), meanAge = mean(age))
#meanCostume <- summarise(group_by(hw, Costume), meanCandies = mean(candy_pieces))
#meanCostume2 <- summarise(group_by(hw2, Costume), meanAge = mean(age))
#meanCostume$Age <- subset(meanCostume2, select = meanAge)
meanCostume$Type <- c("Scary", "Not scary", "Not scary", "Scary", "Not scary", "Not scary", "Scary", "Not scary", "Scary") # wasnt sure how to keep a Type row so just made a new one
meanCostume$Type <- as.factor(meanCostume$Type) # make sure Type is a factor
str(meanCostume)
```

graph of the means where y = candies taken and x = age with color showing Type of costume

```{r}
ggplot(meanCostume, aes(x = meanAge, y = meanCandies, color = Type)) + geom_point(size = 5) + xlab("Mean Age of Kids(years)") + ylab("Mean Number of Candies Taken")
```
You got there, but definately made it complicated. You could use `group_by()` with both costume and type e.g. `group_by(Costume, Type)` and then summarise and it would get you to the data frame you need more efficiently.

Also, in  your `summarise()` statement, for `mean()` you should include `na.rm = T` and that will take care of your NA issue.


make a new DF to look at just not scary costumes and under 10.  then plot it with a histogram

```{r}
YNS <- filter(halloween, Type == "Not scary" & age <= 10) # YNS = young not scary
ggplot(YNS, aes(x = age,)) + geom_histogram(binwidth = 2) + ylab("Number")
```

make a box plot with x = age and y = costume. separate it with facet_wrap by type.
put light grey see though points on the plot. didnt use coord_flip() just switched x and y

```{r}
ggplot(halloween, aes(x = age, y = Costume)) + geom_boxplot() + geom_point(size = 4, color = 'lightgrey', alpha = 0.5) + xlab("Child age (years)") + ylab("Costume  choice") + theme_bw() + facet_wrap(~Type)
```

