---
title: "Using dplyr to fix mistakes"
author: "HarrySecor"
date: "10/2/2022"
output: html_document
---

make sure to bring in the regular clear and librarys code

```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

import the needed CSV file without stringsAsFactors
also give a summary of DF

```{r}
DF <- read.csv(here("Data", "drug_resistance.csv"))
summary(DF)
levels(DF)
```

re-import the needed CSV file with stringsAsFactors = TRUE
also give a summary of DF

```{r}
DF <- read.csv(here("Data", "drug_resistance.csv"), stringsAsFactors = TRUE)
summary(DF)
levels(DF)
```

without stringsAsFactors
there are no difference in the treatment or tech.name columns and it doesn't have much information on them

with stringsAsFactors
in treatment and tech.name there is some data that can be condensed as they are the same just with spelling errors. 
a difference in capitalization or just a different way it was written 

both
the numbers are the same for Plate_n and colony.count

levels returns null for both and unique returns essentially DF

start with treatment because already sorted into rows 
1-10 control, 11-20 drug x 2, 21-30 drug x 3

```{r}
DF$Treatment[1:10] <- "control"
DF$Treatment[11:20] <- "drug x 2"
DF$Treatment[21:30] <- "drug x 3"
```

see what actually need to be done for tech.name
Brian can't spell his name 
Becca's isn't consistent with capitalization 
the others are actually fine

```{r}
DF$tech.name[4] <- "Brian"
DF$tech.name[15] <- "Brian"
DF$tech.name[21:23] <- "Brian"
DF$tech.name[14] <- "Becca"
DF$tech.name[19] <- "Becca"
```

to test work call summary of DF looks better

```{r}
DF$Treatment <- factor(DF$Treatment)
DF$tech.name <- factor(DF$tech.name)
summary(DF)
```
