---
title: "Applying more dplyr to my data"
author: "HarrySecor"
date: "9/29/2022"
output: html_document
---

the goal is to reinforce concepts from GSWR Chapter 2 and Chapter 3 and to push you to apply functions from the dplyr package more independently

have a code fragment to clear R 
try to keep  the answers for each question in a separate code fragment


```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

get the data into a R Data-Frame

```{r}
DF <- read.csv(here("Data", "day_one_data_for_homework13.csv"), stringsAsFactors = TRUE)
```

view said data frame

```{r}
View(DF)
```

rename the names of the column headers to look better and make better sense 

```{r}
names(DF) <- c("Name", "Date", "Part", "Tree_num", "Species", "leaf_length", "leaf_width", "leaf_units")
```

make a seperate data frame for measurements in inches called English (should be imperial)

```{r}
English <- filter(DF, leaf_units == "inches" )
```

I'm not sure if this is asking to take all the dates and make them uniform 
or to leave the dates as is and just group them in there different formats

```{r}
Dates_uniform <- mutate(DF, Date = "8/24/2022")

Uniform_dates <- arrange(DF, Date, group_by = TRUE)
```


