---
title: "Secor_homework_19"
author: "HarrySecor"
date: "10/16/2022"
output: html_document
---

# Homework 19 

## else section of the homework

### main notes

I just went down through the homework and abbreviated it in to the 7 steps of R code below
I tried to keep each R code chunk simple doing one to two real commands each
There were honestly a few things I had to look up because I did not remember how exactly to do them

# list of steps

step 1: enter the initial setup code to import libraries and to clear R's memory

```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```

step 2: import the leaf data into a data set called Leaves

```{r}
Leaves <- read.csv(here("Data", "Class_leaf_measurements.csv"), stringsAsFactors = F)
```

step 3: use the str() function on Leaves

```{r}
str(Leaves)
```

step 4: use the names function to rename the column headers to make them look good and make sense

```{r}
names(Leaves) <- c("Tree_num", "Species", "Leaf_num", "DBH_cm", "Petiole_length", "Total_lenght_cm", "Middle_lobe_lenght_cm", "Middle_lobe_width_cm", "Person")
```

step 5: convert species into a factor variable and make sure all the names are Norway maple, Red maple, or Sugar maple
I looked through the data to see where the problems were and sorted them by tree so that's why they are in a weird order

```{r}
Leaves$Species[121:130] <- "Norway maple"
Leaves$Species[11:20] <- "Red maple"
Leaves$Species[131:140] <- "Red maple"
Leaves$Species[141:150] <- "Sugar maple"
Leaves$Species[21:30] <- "Sugar maple"
Leaves$Species <- as.factor(Leaves$Species)
```

step 6: create a new data frame with just sugar maple data called Sugar without Person, Leaf_num, and Tree_num
looked up ways to delete columns and go the second line of code as the result

```{r}
Sugar <- filter(Leaves, Species == "Sugar maple")
Sugar <- subset(Sugar, select = -c(Tree_num, Leaf_num, Person))
```

step 7: make a histogram of the petiole data from the Sugar data frame
im not sure if we have gone though how to make a histogram that or I fogot so I looked it up

```{r}
ggplot(Sugar, aes(x=Petiole_length)) + geom_histogram()
```

